%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% Template: https://github.com/posquit0/Awesome-CV
% License: CC BY-SA 4.0

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{awesome-cv}
\usepackage{textcomp}
\fontdir[fonts/]
\newcommand*{\sectiondir}{resume/}
\colorlet{awesome}{awesome-red}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
  \headerlastnamestyle{Juan Tamayo} \\
  \vspace{2mm}
  \href{mailto:juancyepest@gmail.com}{juancyepest@gmail.com}  |  +57 3174444258  |  Colombia \\
  \href{https://github.com/tamayotchi}{github.com/tamayotchi}  |  \href{https://www.linkedin.com/in/juantamayo26/}{linkedin.com/in/juantamayo26}  |  \href{https://tamayotchi.com/}{tamayotchi.com}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Skills}
\begin{center}
  \setlength\tabcolsep{1ex}
  \setlength{\extrarowheight}{0pt}
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} r L{14.7cm}}
    \skilltypestyle{Languages} & \skillsetstyle{TypeScript, JavaScript, Elixir, Python, C, C++, SQL} \\
    \skilltypestyle{Backend} & \skillsetstyle{Node.js, Phoenix LiveView, REST APIs} \\
    \skilltypestyle{Cloud} & \skillsetstyle{AWS, GCP Cloud Run, Cloudflare} \\
    \skilltypestyle{Data} & \skillsetstyle{PostgreSQL, DynamoDB} \\
    \skilltypestyle{Integrations} & \skillsetstyle{OpenAI, Whisper, Mercado Pago} \\
    \skilltypestyle{Tools} & \skillsetstyle{Terraform, Docker, Git, CI/CD} \\
    \skilltypestyle{Engineering} & \skillsetstyle{Clean code, clean architecture, system design, API design, performance tuning, production debugging} \\
    \skilltypestyle{Spoken} & \skillsetstyle{Spanish (Native), English (B2)}
  \end{tabular*}
\end{center}
\vspace{-5mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
  \cventry
  {Backend Engineer (Mid Level to Senior)}
  {Instaleap / Instacart}
  {Remote / Colombia}
  {Jul. 2021 -- Present}
  {\begin{cvitems}
    \item {Joined as a Mid Level Backend Engineer and was promoted to Senior Backend Engineer in 2025 after taking ownership of critical production logistics and ecommerce backend services.}
    \item {Build horizontally scalable services with AWS, Terraform, and PostgreSQL; optimize queries and workflows to improve latency, reliability, and stability in high volume delivery operations.}
    \item {Design delivery-optimization algorithms, debug critical incidents, ship backend features, collaborate with product, frontend, data, QA, and operations teams, and mentor junior engineers.}
  \end{cvitems}}

  \cventry
  {Teaching Assistant (Part-Time)}
  {Universidad Tecnológica de Pereira}
  {Pereira, Colombia}
  {Feb. 2020 -- Sep. 2022}
  {\begin{cvitems}
    \item {Guided students in algorithms and programming concepts through one-on-one support, problem-solving sessions, and code reviews.}
  \end{cvitems}}

  \cventry
  {Freelance Web Developer}
  {Self-employed}
  {Colombia}
  {Feb. 2020 -- Feb. 2021}
  {\begin{cvitems}
    \item {Built and optimized WordPress websites for small business clients, improving speed, SEO, brand consistency, and user experience to support online sales.}
  \end{cvitems}}
\end{cventries}
\vspace{-3mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Projects}
\begin{cventries}
  \cventry
  {Elixir}
  {Prezio}
  {\href{https://prezio.tamayotchi.com/}{prezio.tamayotchi.com}}
  {2025}
  {\begin{cvitems}
    \item {Built a product price-tracking web app that compares store listings, highlights best prices, shows update timestamps, and keeps purchase links one click away.}
  \end{cvitems}}

  \cventry
  {Cloudflare, Mercado Pago}
  {Zapenu}
  {\href{https://zapenu.com/lepancake/gKhixyg}{zapenu.com}}
  {2025}
  {\begin{cvitems}
    \item {Built a menu-commerce platform with a back-office console, multi-tenant API, adaptive customer menu, WhatsApp ordering flows, QR codes per table, menu builder, and payment integration.}
  \end{cvitems}}

  \cventry
  {OpenAI, Whisper, AWS Lambda, GCP Cloud Run, DynamoDB}
  {WhatsApp Reminders}
  {\href{https://github.com/tamayotchi/WhatsAppReminders}{GitHub}}
  {2024}
  {\begin{cvitems}
    \item {Developed a WhatsApp assistant that parses text and voice reminders with OpenAI tool calls and Whisper, stores scheduled reminders, and sends WhatsApp notifications when due.}
  \end{cvitems}}

  \cventry
  {Discord, COD API, AWS EC2}
  {CodTracker Bot}
  {\href{https://github.com/tamayotchi/CodTracker-Bot}{GitHub}}
  {2021}
  {\begin{cvitems}
    \item {Created a Discord bot that registers Warzone players, fetches Call of Duty stats, renders Discord embeds, persists player data, and falls back to scraping when the API is unavailable.}
  \end{cvitems}}

  \cventry
  {Elixir, Phoenix LiveView, PDF generation}
  {Nativo Studio}
  {}
  {2026}
  {\begin{cvitems}
    \item {Built an internal project-management system for projects, payments, inventory, extras, expenses, calendar events, and PDF invoicing.}
  \end{cvitems}}
\end{cventries}
\vspace{-3mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
  \cventry
  {Systems Engineering, GPA: 4.0/5.0}
  {Universidad Tecnológica de Pereira}
  {Pereira, Colombia}
  {}
  {}
\end{cventries}

\end{document}
